Cognate beginnings to bilingual lexical acquisition

### 2023-07-27 index.qmd
Update website

# Cognate beginnings to bilingual lexical acquisition

Gonzalo Garcia-Castro [:bird:](https://twitter.com/gongcastro) [:elephant:](https://fediscience.org/@gongcastro) • Universitat Pompeu Fabra

Daniela S. Avila Varela • Universidade de Lisboa

Ignacio Castillejo [:bird:](https://twitter.com/IndaloNacho) • Universidad Autónoma de Madrid

Nuria Sebastian-Galles • Universitat Pompeu Fabra

-------------------------------------------------

| Link                                                             | Contents                                                       |
|------------------------------------------------------------------|----------------------------------------------------------------|
| [Website](https://gongcastro.github.io/cognate.beginnings)       | Instructions for reproducibility, data dictionaries, lab notes |
| PsyArxiv                                                         | Preprint and figures                                           |
| [GitHub](https://github.com/gongcastro/cognate.beginnings)       | Code, preprint and figures                                     |
| [Open Science Framework](https://osf.io/hy984/)                  | Code, preprint, and results (model outputs)                    |
| [Docker](https://hub.docker.com/r/gongcastro/cognate-beginnings) | Docker image with reproducible RStudio session                 |

>>>>

{{< include README.md >}}
